Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
improve table
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58602 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table*}
  \centering
  \begin{tabular}{|lrl|l|}
    \hline
    \textbf{Rules:} & & 1. m\"{a} $\rightarrow$ min\"{a} \\
     ~              & & 2. oon $\rightarrow$ olen \\
     ~              & & 3. (?+)nkaa $\rightarrow$ \textbackslash1n kanssa \\
    \hline
  \end{tabular}
~\\
~\\
  \begin{tabular}{|l|r|l|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Tomminkaa `I am with Tommi'.} \\
    \hline
    \multirow{2}{*}{Step 1} & & M\"{a} oon Tomminkaa & apply rule 1 \\
                            & & Min\"{a} oon Tomminkaa & \\
    \hline
    \multirow{2}{*}{Step 2} & & M\"{a} oon Tomminkaa & apply rule 2 \\
                            &   & Min\"{a} oon Tomminkaa & \\
                            &   & M\"{a} olen Tomminkaa & \\
                            &   & Min\"{a} olen Tomminkaa & \\
    \hline
    \multirow{2}{*}{Step 3} &   & M\"{a} oon Tomminkaa   & apply rule 3\\
                            &   & Min\"{a} oon Tomminkaa  &\\
                            &   & M\"{a} olen Tomminkaa  &\\
                            &   & Min\"{a} olen Tomminkaa  &\\
                            &   & M\"{a} oon Tommin kanssa  &\\
                            &   & Min\"{a} oon Tommin kanssa  &\\
                            &   & M\"{a} olen Tommin kanssa  &\\
                            &   & Min\"{a} olen Tommin kanssa  &\\
    \hline
    \multirow{2}{*}{Step 4} & -4.5811 &  Min\"{a} olen Tommin kanssa & rank candidates \\
                            & -7.8174 &  Min\"{a} oon Tommin kanssa & \\
                            & -8.0941 &  M\"{a} olen Tommin kanssa & \\
                            & -8.8651&  M\"{a} oon Tommin kanssa & \\
                            & -9.2045 &  Min\"{a} olen Tomminkaa & \\
                            & -12.4408 &  Min\"{a} oon Tomminkaa & \\
                            & -12.7176 &  M\"{a} olen Tomminkaa & \\
                            & -13.4885 &  M\"{a} oon Tomminkaa & \\

>>>>

\begin{table*}
  \centering
  \begin{tabular}{|l|r|l|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Tomminkaa `I am with Tommi'.} \\
    \hline
    \multirow{2}{*}{Step 1} & & M\"{a} oon Tomminkaa & apply rule 1 \\
                            & & Min\"{a} oon Tomminkaa & m\"{a} $\rightarrow$ min\"{a} \\
    \hline
    \multirow{2}{*}{Step 2} & & M\"{a} oon Tomminkaa & apply rule 2 \\
                            &   & Min\"{a} oon Tomminkaa & oon $\rightarrow$ olen \\
                            &   & M\"{a} olen Tomminkaa & \\
                            &   & Min\"{a} olen Tomminkaa & \\
    \hline
    \multirow{2}{*}{Step 3} &   & M\"{a} oon Tomminkaa   & apply rule 3\\
                            &   & Min\"{a} oon Tomminkaa  & (?+)nkaa $\rightarrow$ \textbackslash1n kanssa \\
                            &   & M\"{a} olen Tomminkaa  &\\
                            &   & Min\"{a} olen Tomminkaa  &\\
                            &   & M\"{a} oon Tommin kanssa  &\\
                            &   & Min\"{a} oon Tommin kanssa  &\\
                            &   & M\"{a} olen Tommin kanssa  &\\
                            &   & Min\"{a} olen Tommin kanssa  &\\
    \hline
    \multirow{2}{*}{Step 4} & -4.5811 &  Min\"{a} olen Tommin kanssa & rank candidates \\
                            & -7.8174 &  Min\"{a} oon Tommin kanssa & \\
                            & -8.0941 &  M\"{a} olen Tommin kanssa & \\
                            & -8.8651&  M\"{a} oon Tommin kanssa & \\
                            & -9.2045 &  Min\"{a} olen Tomminkaa & \\
                            & -12.4408 &  Min\"{a} oon Tomminkaa & \\
                            & -12.7176 &  M\"{a} olen Tomminkaa & \\
                            & -13.4885 &  M\"{a} oon Tomminkaa & \\
